\documentclass[11pt]{article}
\usepackage{graphicx} 
\usepackage{fontawesome}
\setlength{\parindent}{0pt}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage[left=1.06cm,
top=1.7cm,
right=1.06cm,
bottom=0.49cm]{geometry}

\begin{document}
% \vspace{-10pt}
\begin{center}
    \scalebox{4}{\textbf{Saakar K.C}} \\
    \hrulefill
\end{center}

\begin{center}
{\large \faMapMarker \ Dillibazar, Kathmandu, Nepal \hspace{6pt} \faEnvelope \ saakar18@gmail.com \hspace{5pt} \faPhone \ +977 9860913736}

\end{center}

\vspace{0.5pt}

\begin{center}
    {\huge \textbf{Education}}
\end{center}
\vspace{-15pt}
        \hrulefill

\textbf{Kathmandu University}, Dhulikhel, Kavre \hfill 2019-Present

Bachelor's degree in Computer Science
% \hfill Graduation Date  [Note: Optional]



\vspace{12pt}

\textbf{Kathmandu Model Secondary School}\hspace{1mm}, Bagbazar, Kathmandu \hfill 2018



National Examination Board(NEB)

\vspace{12pt}

\textbf{Meridian International School}, Baluwatar, Kathmandu \hfill	2016
\\
Secondary Education Examination (SEE)

\vspace{12pt}

\begin{center}
    {\Huge\textbf{Experience}}
\end{center}
\vspace{-15pt}

        \hrulefill

% \textbf{University Projects} 


\begin{itemize}[noitemsep]

    \item\hspace{-5pt}{\Large\textbf{ Analysis Of Exploratory Data On Recruitment Data}} \\
              Executed comprehensive data processing and visualization in Univariate Non-Graphical EDA, utilizing Python with Pandas and Numpy  to analyze the Recruitment data.
          \\

    \item {\Large\textbf{Data Analysis And Visualization Of Covid-19 Data}} \\
              Conducted comprehensive data analysis and visualization of Covid-19 data, employing Python for data preprocessing and cleaning, followed by detailed Graphical Exploratory Data Analysis (EDA) to identify trends and patterns using Python and Streamlit for dashboard.
            \\
    \item {\Large\textbf{HCI Research Paper Using Schneiderman’s Eight Golden Rules}} \\
          Utilized ethnographic research to inform enhancements through the lens of Human-Centered Design and usability principles, while leveraging insights from cognitive psychology and user feedback to optimize digital product usability.
          \\
            

            
    \item {\Large\textbf{Bhozzan Mobile Application}} \\
          Built a React Native application for food delivery, featuring an intuitive admin control interface tailored for restaurants, to ensure smooth operations and enhance user experience.
            \\
          
    \item {\Large\textbf{CryptoMart}} \\
             Enabled seamless purchasing of items with cryptocurrency through integration with MetaMask as a secure and efficient payment platform, ensuring smooth transactions and enhanced user convenience.
            \\
          
    \item {\Large\textbf{BlogNepal}} \\
          Created a web-based application for blog writing with HTML, CSS, and JavaScript, focusing on user experience and fostering creativity.
        \\
          
    \item {\Large\textbf{Auction House}}\\
             Built a web-based auctioning platform using React and Firebase, enabling smooth bidding processes and real-time updates for sellers and bidders, ensuring efficient transactions and user satisfaction.
             \\

    \clearpage
           
          
\end{itemize} 





% \textbf{Organization} \hfill City, State (or Remote)

% \textbf{Position Title} \hfill Month Year – Month Year
% \begin{itemize}[noitemsep]
%     \item With your next-most recent position, describe your experience, skills, and resulting outcomes in bullet or paragraph form.
%     \item Begin each line with an action verb and include details that will help the reader understand your accomplishments, skills, knowledge, abilities, or achievements.
%     \item Quantify where possible.
%     \item Do not use personal pronouns; each line should be a phrase rather than a full sentence.
% \end{itemize}
\vspace{-10pt}
\begin{center}
    {\Huge\textbf{Leadership \& Activities}}
\end{center}
\vspace{-15pt}
\hrulefill
\vspace{3pt}

% \textbf{Kathmandu University Computer Club:}	

{\Large\textbf{Kathmandu University Computer Club Sports Coordinator}} \hfill 2023-2024
\begin{itemize}[noitemsep]
    \item Spearheaded the development of crucial management skills such as effective people management, meticulous budgeting, and efficient time management within the role.
    
    \item Demonstrated and honed leadership capabilities by overseeing and coordinating sports-related activities, ensuring smooth execution and fostering a collaborative environment.
\end{itemize} 

\\

{\Large\textbf{Red-Cross in Kathmandu University Member } }\hfill2019-2021
\begin{itemize}[noitemsep]
    
    \item Developed effective communication skills while working collaboratively with diverse teams and interacting with community members during awareness campaigns.
    
    \item Refined problem-solving skills through active participation in various humanitarian projects, successfully tackling and resolving a multitude of challenges encountered during relief efforts.


    
    \item Gained organizational skills through the coordination of events such as blood drives and health camps, ensuring seamless execution and maximum impact.
\end{itemize}
\\
{\Large\textbf{Winner in Inter-Departmental Model Competition for BlogNepal}} \hfill2021
\begin{itemize}[noitemsep]
    \item 
Featured project presentation at Sankalpa 2021, held at Kathmandu University, providing valuable insights and solutions to a wide-ranging audience.
    \
\end{itemize}
\\

\begin{center}
    {\Huge\textbf{Publications}}
    
    \begin{itemize}[noitemsep]
    \hrulefill
    \item K.C, S., Thapaliya, S., Pradhanang, S., Bhandari, K., Acharya, A. (2023).\textit{ UI Enhancement of
Online Rental Applications with the Implementation of Schneiderman’s Eight Golden}
Rules. Unpublished manuscript.
    \vspace{5mm}
    \item K.C, S., Pradhanang, S. (2023).\textit{ Data visualization for COVID-19 tracking: With Streamlit,
Pandas, and Plotly.} Unpublished manuscript.

    \vspace{5mm}

     \item K.C, S. (2023).\textit{ Exploratory Data Analysis and Data Visualization of Recruitment Data: With Numpy, Pandas, and Plotly.} Unpublished manuscript


         

\end{itemize} 
\end{center}


\begin{center}
    {\Huge\textbf{Skills \& Interests}}
\end{center}
\vspace{-15pt}

\hrulefill \\
{\large\textbf{Technical:}} Python, SQL, Pandas, Numpy, Matplotlib, LaTeX, HTML, CSS, Javascript, C++, REACT, NEXT

{\large\textbf{Language:}} Nepalese, English, Hindi 

{\large\textbf{Interests:}} Data Science, Data Engineering, Machine Learning, Web Development, Basketball, Football




\end{document}
